Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-09-18 WSSSPE4_report/WSSSPE4_report.tex
adding moore gift number

% NSF grant for WSSSPE4
This material is based upon work supported by the National Science
Foundation under grant ACI-1648293, by the Gordon and Betty Moore Foundation under gift \todo{check to see if there's a number}, and by the Alfred P.~Sloan Foundation
under grant G-2016-7214.

>>>>

% NSF grant for WSSSPE4
This material is based upon work supported by the National Science
Foundation (ACI-1648293), by the Gordon and Betty Moore Foundation  (GBMF\#5620), and by the Alfred P.~Sloan Foundation (G-2016-7214).
